Figures

### 2018-03-27 scripts/analysis.Rmd
adjust fig size

```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE}

>>>>

```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE, fig.width = 4.8, fig.height = 3.6}
